A reproducible journal article with RMarkdown: A building science template with examples for beginners based on the Elsevier journal format

### 2020-06-12 Paper/Manuscript.tex
Re-knit w/ fixing name of graphic

\documentclass[]{elsarticle} %review=doublespace preprint=single 5p=2 column
%%% Begin My package additions %%%%%%%%%%%%%%%%%%%
\usepackage[hyphens]{url}
\usepackage{lineno} % add
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}

\bibliographystyle{elsarticle-harv}
\biboptions{sort&compress} % For natbib
\usepackage{graphicx}
\usepackage{booktabs} % book-quality tables
%% Redefines the elsarticle footer
%\makeatletter
%\def\ps@pprintTitle{%
% \let\@oddhead\@empty
% \let\@evenhead\@empty
% \def\@oddfoot{\it \hfill\today}%
% \let\@evenfoot\@oddfoot}
%\makeatother

% A modified page layout
\textwidth 6.75in
\oddsidemargin -0.15in
\evensidemargin -0.15in
\textheight 9in
\topmargin -0.5in
%%%%%%%%%%%%%%%% end my additions to header

\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \usepackage{fontspec}
  \ifxetex
    \usepackage{xltxtra,xunicode}
  \fi
  \defaultfontfeatures{Mapping=tex-text,Scale=MatchLowercase}
  \newcommand{\euro}{€}
\fi
% use microtype if available
\IfFileExists{microtype.sty}{\usepackage{microtype}}{}
\usepackage[left=2.5cm,right=2.5cm,top=2.5cm,bottom=2.5cm]{geometry}
\usepackage{longtable}
\usepackage{graphicx}
% We will generate all images so they have a width \maxwidth. This means
% that they will get their normal width if they fit onto the page, but
% are scaled down if they would overflow the margins.
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth
\else\Gin@nat@width\fi}
\makeatother
\let\Oldincludegraphics\includegraphics
\renewcommand{\includegraphics}[1]{\Oldincludegraphics[width=\maxwidth]{#1}}
\ifxetex
  \usepackage[setpagesize=false, % page size defined by xetex
              unicode=false, % unicode breaks when used with xetex
              xetex]{hyperref}
\else
  \usepackage[unicode=true]{hyperref}
\fi
\hypersetup{breaklinks=true,
            bookmarks=true,
            pdfauthor={},
            pdftitle={A reproducible journal article with RMarkdown: A building science template with examples for beginners based on the Elsevier journal format},
            colorlinks=true,
            urlcolor=blue,
            linkcolor=blue,
            pdfborder={0 0 0}}
\urlstyle{same}  % don't use monospace font for urls
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\setcounter{secnumdepth}{5}
\usepackage{setspace}
\doublespacing
\usepackage[font={small}]{caption}
% Pandoc toggle for numbering sections (defaults to be off)
% Pandoc header
\usepackage{setspace}
\doublespacing
\usepackage[font={small}]{caption}

\usepackage[nomarkers]{endfloat}

@@

  \title{A reproducible journal article with RMarkdown: A building science
template with examples for beginners based on the Elsevier journal
format}
    \author[CBE]{Paul Raftery\corref{c1}}
   \ead{p.raftery@berkeley.edu} 
   \cortext[c1]{Corresponding Author}
    \author[CBE]{Dana Miller}

@@

\textbf{Graphical Abstract}\\
\includegraphics{C:/Users/Dana/3_Professional/CBE/Reproducibility/cbe-rmd-example/Paper/SupplementaryMaterial/Images/Latex_logo.png}

@@

\section{Introduction}\label{introduction}

The purpose of this (very much work-in-progress) document is to provide
a complete R markdown template for an Elsevier journal submission (based
on the rticles repository Allaire et al.
(\protect\hyperlink{ref-rticles}{2017})), along with useful examples and
packages to improve usability for folks who are just starting out with
this workflow. The eventual intent is to capture minimal examples of the
common things that authors need to do when writing papers in R markdown;
provide examples of useful packages, workflows, and tools; and provide
solutions to common issues that folks encounter.

@@

\section{\texorpdfstring{Methods (this is a `level 1
heading')}{Methods (this is a level 1 heading)}}\label{methods-this-is-a-level-1-heading}

\subsection{\texorpdfstring{Markdown (this is a `level 2
heading')}{Markdown (this is a level 2 heading)}}\label{markdown-this-is-a-level-2-heading}

@@

\subsubsection{Level 3 heading}\label{level-3-heading}

@@

\subsection{Tables}\label{tables}

Here is an example of a table created from the .csv file in the
\texttt{SupplementaryMaterial/Data}folder using the \texttt{gt} package
from RStudio. You can read more about \texttt{gt}
\href{https://github.com/rstudio/gt}{here}, and there's helpful examples
to further customize tables (eg with color, foototes, significant
figures, re-labeling columns, and more)
\href{https://github.com/allisonhorst/gt-awesome-tables}{here}.

\captionsetup[table]{labelformat=empty,skip=1pt}

\begin{longtable}{lrrc}
\caption*{
\large Example irises\\ 
\small Data on five randomly selected irises\\ 
} \\ 
\toprule
iris\_class & sepal\_length & petal\_length & petal\_length\_level \\ 
\midrule
Iris-virginica & 6.4 & 5.5 & High \\ 
Iris-virginica & 6.9 & 5.4 & High \\ 
Iris-setosa & 4.4 & 1.3 & VeryLow \\ 
Iris-virginica & 7.7 & 6.7 & VeryHigh \\ 
Iris-versicolor & 5.0 & 3.3 & Medium \\ 
\bottomrule
\end{longtable}

\subsection{Cross-referencing}\label{cross-referencing}

@@

\begin{figure}
\centering
\includegraphics{C:/Users/Dana/3_Professional/CBE/Reproducibility/cbe-rmd-example/Paper/SupplementaryMaterial/Images/Correlation.png}
\caption{\label{fig:correlation}Correlation. Source: XKCD, xkcd.com/552}
\end{figure}

\subsection{Calculations in text}\label{calculations-in-text}

@@

\subsection{Citations}\label{citations}

Citing other literature is remarkably easy, just like this Coakley,
Raftery, \& Keane
(\protect\hyperlink{ref-coakleyReviewMethodsMatch2014}{2014}). This
citation key references the tag associated with an entry in
Bibliography.bib (a BibTex file). I've found it easiest to use Zotero to
manage my library of references and to generate the BibTex file, though
any software that creates a valid BibTex file should work fine. Zotero
allows you to create a `Collection' (or folder) that gathers together
all of the references used for a particular document. When combined with
with the Better BibTex plugin, that collection can be exported to a
BibTex file that is continually updated as you add or edit references in
that Collection. Better BibTex also puts the citation key - the text
after the `@' sybmbol in the .Rmd file - on the upper right of each
entry, which is convenient for adding citations.

@@

The instructions for installing BetterBibtex are
\href{https://retorque.re/zotero-better-bibtex/}{here}.

\subsubsection{Citing software}\label{citing-software}

It is also good practice to include citations not such for literature
like journal articles and reports, but also the software used in the
analysis. Many software packages have accompanying publications that can
be cited, and even if they don't it is important to attribute which
version and which software you used. Citing software helps to provide
credit for the creators and maintainors of the software and demonstrate
that people (like you!) are using the software, which is especially
important for open-source tools supported through public research
funding.

You can use the \texttt{greatful} package to quickly generate a list of
the packages for software used in an R project using the
\texttt{cite\_packages} function from \texttt{greatful}. There is an
additional function called \texttt{get\_citations} that generates the
Bibtex-formatted citations for each package. It's not elegant, but you
can use the first to list packages used, then generate the
\texttt{pkg-refs.bib} file (saved to
\texttt{/Paper/SuplementaryMaterial} by default in this template), copy
the content into your overall \texttt{Bibliography.bib} file for the
whole document, and then cite the packages in your document as you would
another source, eg by using \texttt{@base} for an in-text citation for
core R software before other packages are installed (also known as `base
R').

\begin{itemize}
\tightlist
\item
  base R - R Core Team (\protect\hyperlink{ref-base}{2018})
\item
  ggpmisc - Aphalo (\protect\hyperlink{ref-ggpmisc}{2016})
\item
  grateful - Rodriguez-Sanchez (\protect\hyperlink{ref-grateful}{2018})
\item
  gt - Iannone, Cheng, \& Schloerke (\protect\hyperlink{ref-gt}{2019})
\item
  here - Müller (\protect\hyperlink{ref-here}{2017})
\item
  knitr - Xie (\protect\hyperlink{ref-knitr}{2018})
\item
  tidyverse - Wickham (\protect\hyperlink{ref-tidyverse}{2017})
\item
  rticles - Allaire et al. (\protect\hyperlink{ref-rticles}{2017})
\item
  bookdown - Xie (\protect\hyperlink{ref-bookdown}{2016})
\item
  rmarkdown - Allaire et al. (\protect\hyperlink{ref-rmarkdown}{2018})
\end{itemize}

\subsection{Equations and math}\label{equations-and-math}

@@

\subsection{Other packages}\label{other-packages}

@@

\subsection{Writing style}\label{writing-style}

@@

\begin{itemize}
\tightlist
\item
  Nature: ``Nature journals like authors to write in the active voice
  (`we performed the experiment\ldots{}') as experience has shown that
  readers find concepts and results to be conveyed more clearly if
  written directly.''(``Nature - How to write a paper,'' n.d.)
\item
  Science: ``Use active voice when suitable, particularly when necessary
  for correct syntax (e.g., `To address this possibility, we constructed
  a lZap library \ldots{},' not `To address this possibility, a lZap
  library was constructed\ldots{}').'' Ruben, 2012, \& Am
  (\protect\hyperlink{ref-rubenHowWriteScientist2012}{2012})
\end{itemize}

@@

\subsubsection{A fun way to spot passive
voice:}\label{a-fun-way-to-spot-passive-voice}

If you can add the words `by zombies' (``A scary-easy way to help you
find passive voice!''
\protect\hyperlink{ref-ScaryeasyWayHelp2014}{2014}) to the end of the
sentence and the sentence still makes logical sense, then the sentence
is in passive voice. You can also switch on the grammar settings in
Microsoft Word's spelling and grammar checker and it will show up that
way.

@@

\section{Results}\label{results}

\subsection{Scatter plot example}\label{scatter-plot-example}

@@

\subsection{Violin plot example}\label{violin-plot-example}

@@

\section{Discussion}\label{discussion}

\section{Limitations}\label{limitations}

@@

\begin{itemize}
\tightlist
\item
  Whether or not figures are included inline with text appears to depend
  of the version of LaTeX the document is compiled with. Compiling on a
  computer where TinyTeX is installed (eg in the Binder associated with
  the reporsitory for this project on GitHub) will render the figures
  inline, whereas compiling the same document on a Windows computer with
  MikTeX installed does not
\item
  Does not include instructions on how to align figures
\end{itemize}

\section{Conclusion}\label{conclusion}

\section{Acknowledgements}\label{acknowledgements}

@@

\section{Declaration of interest}\label{declaration-of-interest}

Descibe any relevant interests of the authors, particularly if there is
a link to the research that is relatively uncommon and could be
perceived as a conflict of interest. Otherwise : All authors declare no
conflict of interest.

\section*{References}\label{references}
\addcontentsline{toc}{section}{References}

\hypertarget{refs}{}
\hypertarget{ref-ScaryeasyWayHelp2014}{}
A scary-easy way to help you find passive voice! (2014). \emph{A
scary-easy way to help you find passive voice! \textbar{} Grammarly
Blog}.
https://www.grammarly.com/blog/a-scary-easy-way-to-help-you-find-passive-voice/.

\hypertarget{ref-rticles}{}
Allaire, J., R Foundation, Wickham, H., Journal of Statistical Software,
Xie, Y., Vaidyanathan, R., \ldots{} Yu, M. (2017). \emph{Rticles:
Article formats for r markdown}. Retrieved from
\url{https://CRAN.R-project.org/package=rticles}

\hypertarget{ref-rmarkdown}{}
Allaire, J., Xie, Y., McPherson, J., Luraschi, J., Ushey, K., Atkins,
A., \ldots{} Chang, W. (2018). \emph{Rmarkdown: Dynamic documents for
r}. Retrieved from \url{https://CRAN.R-project.org/package=rmarkdown}

\hypertarget{ref-ggpmisc}{}
Aphalo, P. J. (2016). \emph{Learn r ...as you learnt your mother
tongue}. Leanpub. Retrieved from \url{https://leanpub.com/learnr}

\hypertarget{ref-coakleyReviewMethodsMatch2014}{}
Coakley, D., Raftery, P., \& Keane, M. (2014). A review of methods to
match building energy simulation models to measured data.
\emph{Renewable and Sustainable Energy Reviews}, \emph{37}(Supplement
C), 123--141. \url{https://doi.org/10.1016/j.rser.2014.05.007}

\hypertarget{ref-gt}{}
Iannone, R., Cheng, J., \& Schloerke, B. (2019). \emph{Gt: Easily create
presentation-ready display tables}. Retrieved from
\url{https://github.com/rstudio/gt}

\hypertarget{ref-klenbortMarkednessPerspectiveInterpretation1974}{}
Klenbort, I., \& Anisfeld, M. (1974). Markedness and perspective in the
interpretation of the active and passive voice. \emph{Quarterly Journal
of Experimental Psychology}, \emph{26}(2), 189--195.
\url{https://doi.org/10.1080/14640747408400404}

\hypertarget{ref-here}{}
Müller, K. (2017). \emph{Here: A simpler way to find your files}.
Retrieved from \url{https://CRAN.R-project.org/package=here}

\hypertarget{ref-NatureHowWrite}{}
Nature - How to write a paper. (n.d.).
https://www.nature.com/authors/author\_resources/how\_write.html.

\hypertarget{ref-base}{}
R Core Team. (2018). \emph{R: A language and environment for statistical
computing}. Vienna, Austria: R Foundation for Statistical Computing.
Retrieved from \url{https://www.R-project.org/}

\hypertarget{ref-grateful}{}
Rodriguez-Sanchez, F. (2018). \emph{Grateful: Facilitate citation of r
packages}. Retrieved from \url{https://github.com/Pakillo/grateful}

>>>>

\documentclass[]{elsarticle} %review=doublespace preprint=single 5p=2 column
%%% Begin My package additions %%%%%%%%%%%%%%%%%%%
\usepackage[hyphens]{url}

  \journal{Building and Environment} % Sets Journal name

\usepackage{lineno} % add
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}

\usepackage{graphicx}
\usepackage{booktabs} % book-quality tables
%%%%%%%%%%%%%%%% end my additions to header

\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \usepackage{fontspec}
  \ifxetex
    \usepackage{xltxtra,xunicode}
  \fi
  \defaultfontfeatures{Mapping=tex-text,Scale=MatchLowercase}
  \newcommand{\euro}{€}
\fi
% use microtype if available
\IfFileExists{microtype.sty}{\usepackage{microtype}}{}
\usepackage[left=2.5cm,right=2.5cm,top=2.5cm,bottom=2.5cm]{geometry}
\bibliographystyle{elsarticle-harv}
\usepackage{color}
\usepackage{fancyvrb}
\newcommand{\VerbBar}{|}
\newcommand{\VERB}{\Verb[commandchars=\\\{\}]}
\DefineVerbatimEnvironment{Highlighting}{Verbatim}{commandchars=\\\{\}}
% Add ',fontsize=\small' for more characters per line
\usepackage{framed}
\definecolor{shadecolor}{RGB}{248,248,248}
\newenvironment{Shaded}{\begin{snugshade}}{\end{snugshade}}
\newcommand{\AlertTok}[1]{\textcolor[rgb]{0.94,0.16,0.16}{#1}}
\newcommand{\AnnotationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\AttributeTok}[1]{\textcolor[rgb]{0.77,0.63,0.00}{#1}}
\newcommand{\BaseNTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
\newcommand{\BuiltInTok}[1]{#1}
\newcommand{\CharTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\CommentTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textit{#1}}}
\newcommand{\CommentVarTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\ConstantTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\ControlFlowTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{\textbf{#1}}}
\newcommand{\DataTypeTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{#1}}
\newcommand{\DecValTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
\newcommand{\DocumentationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\ErrorTok}[1]{\textcolor[rgb]{0.64,0.00,0.00}{\textbf{#1}}}
\newcommand{\ExtensionTok}[1]{#1}
\newcommand{\FloatTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
\newcommand{\FunctionTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\ImportTok}[1]{#1}
\newcommand{\InformationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\KeywordTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{\textbf{#1}}}
\newcommand{\NormalTok}[1]{#1}
\newcommand{\OperatorTok}[1]{\textcolor[rgb]{0.81,0.36,0.00}{\textbf{#1}}}
\newcommand{\OtherTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{#1}}
\newcommand{\PreprocessorTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textit{#1}}}
\newcommand{\RegionMarkerTok}[1]{#1}
\newcommand{\SpecialCharTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\SpecialStringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\StringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\VariableTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\VerbatimStringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\WarningTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\usepackage{longtable}
\ifxetex
  \usepackage[setpagesize=false, % page size defined by xetex
              unicode=false, % unicode breaks when used with xetex
              xetex]{hyperref}
\else
  \usepackage[unicode=true]{hyperref}
\fi
\hypersetup{breaklinks=true,
            bookmarks=true,
            pdfauthor={},
            pdftitle={A reproducible journal article with RMarkdown: A building science template with examples for beginners based on the Elsevier journal format},
            colorlinks=true,
            urlcolor=blue,
            linkcolor=blue,
            pdfborder={0 0 0}}
\urlstyle{same}  % don't use monospace font for urls

\setcounter{secnumdepth}{5}
% Pandoc toggle for numbering sections (defaults to be off)

% Pandoc header
\usepackage{setspace}
\doublespacing
\usepackage[font={small}]{caption}
\usepackage{amsmath}
\usepackage{booktabs}
\usepackage{caption}
\usepackage{longtable}

@@

  \title{A reproducible journal article with RMarkdown: A building science template with examples for beginners based on the Elsevier journal format}
    \author[CBE]{Paul Raftery\corref{Corresponding Author}}
   \ead{p.raftery@berkeley.edu} 
    \author[CBE]{Dana Miller}

@@

\textbf{Graphical Abstract}

\includegraphics[width=4.44in]{/home/trc/rmd-example/Paper/SupplementaryMaterial/Images/Latex_logo}

@@

\hypertarget{introduction}{%
\section{Introduction}\label{introduction}}

The purpose of this (very much work-in-progress) document is to provide a complete R markdown template for an Elsevier journal submission (based on the \href{https://github.com/rstudio/rticles}{rticles} repository Allaire et al. (\protect\hyperlink{ref-rticles}{2017})), along with useful examples and packages to improve usability for folks who are just starting out with this workflow. The eventual intent is to capture minimal examples of the common things that authors need to do when writing papers in R markdown; provide examples of useful packages, workflows, and tools; and provide solutions to common issues that folks encounter.

@@

\hypertarget{methods-this-is-a-level-1-heading}{%
\section{Methods (this is a `level 1 heading')}\label{methods-this-is-a-level-1-heading}}

\hypertarget{markdown-this-is-a-level-2-heading}{%
\subsection{Markdown (this is a `level 2 heading')}\label{markdown-this-is-a-level-2-heading}}

@@

\hypertarget{level-3-heading}{%
\subsubsection{Level 3 heading}\label{level-3-heading}}

@@

\hypertarget{tables}{%
\subsection{Tables}\label{tables}}

Here is an example of a table created from the .csv file in the \texttt{SupplementaryMaterial/Data}folder using the \texttt{gt} package from RStudio. You can read more about \texttt{gt} \href{https://github.com/rstudio/gt}{here}, and there's helpful examples to further customize tables (eg with color, footnotes, significant figures, re-labeling columns, and more) \href{https://github.com/allisonhorst/gt-awesome-tables}{here}.

\captionsetup[table]{labelformat=empty,skip=1pt}
\begin{longtable}{lrrc}
\caption*{
\large Example irises\\ 
\small Data on five randomly selected irises\\ 
} \\ 
\toprule
iris\_class & sepal\_length & petal\_length & petal\_length\_level \\ 
\midrule
Iris-setosa & 5.3 & 1.5 & Low \\ 
Iris-versicolor & 5.6 & 3.6 & Medium \\ 
Iris-versicolor & 6.1 & 4.7 & High \\ 
Iris-virginica & 6.7 & 5.2 & High \\ 
Iris-virginica & 5.6 & 4.9 & High \\ 
\bottomrule
\end{longtable}

\hypertarget{spellcheck}{%
\subsection{Spellcheck}\label{spellcheck}}

If you are using RStudio, press F7 or go to \texttt{Edit} --\textgreater{} \texttt{Check\ spelling} in the menu.

\hypertarget{cross-referencing}{%
\subsection{Cross-referencing}\label{cross-referencing}}

@@

\begin{figure}[h]
\includegraphics[width=0.92in]{/home/trc/rmd-example/Paper/SupplementaryMaterial/Images/correlation} \caption{Correlation. Source: XKCD, xkcd.com/552}\label{fig:correlation}
\end{figure}

\hypertarget{calculations-in-text}{%
\subsection{Calculations in text}\label{calculations-in-text}}

@@

\hypertarget{citations}{%
\subsection{Citations}\label{citations}}

\hypertarget{citing-literature}{%
\subsubsection{Citing literature}\label{citing-literature}}

Citing other literature is remarkably easy, just like this Coakley et al. (\protect\hyperlink{ref-coakleyReviewMethodsMatch2014}{2014}). This citation key references the tag associated with an entry in Bibliography.bib (a BibTex file). I've found it easiest to use Zotero to manage my library of references and to generate the BibTex file, though any software that creates a valid BibTex file should work fine. Zotero allows you to create a `Collection' (or folder) that gathers together all of the references used for a particular document. When combined with with the Better BibTex plugin, that collection can be exported to a BibTex file that is continually updated as you add or edit references in that Collection. Better BibTex also puts the citation key - the text after the `@' symbol in the .Rmd file - on the upper right of each entry, which is convenient for adding citations.

@@

\textbf{Step-by-step instructions for creating a new Zotero collection and adding a citation}
1. Install BetterBibtex with the instructions \href{https://retorque.re/zotero-better-bibtex/}{here}.

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\setcounter{enumi}{1}
\item
  First, create a new Zotero collection for this paper in your own Zotero library. You can add existing references by dragging and dropping them into the folder for this collection, or add new references from the web with this collection highlighted.
\item
  In the far left Zotero pane, right-click on the folder for this collection, select ``Export Collection'', and selection ``Better BibTeX'' and the format, and tick the ``Keep updated'' box (this will automatically update the stored .bib file when you add new items to this collection). Save this .bib file in a location together with the document you are working on (in this repository, it's under \texttt{/Paper})

  \begin{itemize}
  \tightlist
  \item
    Note - the dynamic updating \emph{only} works if you export the whole collection to one .bib file, so clicking on the items in the collection and exporting them individually or together will not work
  \end{itemize}
\item
  To add a citation in the text, first make sure that the item is saved in the Zotero collection that is linked to the automatically-updating .bib file for your document. Then click on that item in Zotero and copy the citation key in the right-hand pane (eg \emph{schiavonThermalComfortPerceived2017})
\item
  In your document, paste the citation key preceded by an @ sign, like this: \texttt{@schiavonThermalComfortPerceived2017} in the text where you want the citation to appear. If you want it wrapped in parentheses, do this \texttt{{[}@schiavonThermalComfortPerceived2017{]}}
\end{enumerate}

\hypertarget{citing-software}{%
\subsubsection{Citing software}\label{citing-software}}

It is also good practice to include citations for the software used in your analysis. After all, the software is also one of the tools you used to carry out your research. It is important to attribute which software and which versions you used you used so other people can better understand your methods. There have been cases where running the same analysis code with different versions of the same software produces different results! In addition, citing software helps to provide credit for the creators and maintainers of the software and demonstrate that people are using it, which is especially important for open-source tools supported through public research funding. Just like software often includes a \texttt{LICENSE} file, a good practice is for citation instructions to be included in a \texttt{CITATION} file associated with the project. Many software packages have accompanying publications that can be cited, and if they don't there is usually a project website or code repository.

\textbf{Instructions for adding software citations with \texttt{grateful} and Zotero}

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{# Example of generating BibTex file for the packages listed below}
\CommentTok{# Note the output location is specified }
\CommentTok{# Note tidyverse is not included in the list below because it's a large package to install on Binder, if you are running this on your own computer I recommend including it if you want to cite it}
\NormalTok{pkgs <-}\StringTok{ }\KeywordTok{c}\NormalTok{(}\StringTok{"here"}\NormalTok{, }\StringTok{"knitr"}\NormalTok{, }\StringTok{"ggpmisc"}\NormalTok{, }\StringTok{"gt"}\NormalTok{, }\StringTok{"grateful"}\NormalTok{, }\StringTok{"base"}\NormalTok{, }\StringTok{"rticles"}\NormalTok{, }\StringTok{"bookdown"}\NormalTok{, }
          \StringTok{"rmarkdown"}\NormalTok{)}
\NormalTok{cites <-}\StringTok{ }\NormalTok{grateful}\OperatorTok{::}\KeywordTok{get_citations}\NormalTok{(pkgs, }\DataTypeTok{filename =} \StringTok{"pkg-refs.bib"}\NormalTok{,}
                    \DataTypeTok{out.dir =}  \KeywordTok{here}\NormalTok{(}\StringTok{"/Paper/SupplementaryMaterial/Software_citations"}\NormalTok{) )}
\end{Highlighting}
\end{Shaded}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\setcounter{enumi}{4}
\item
  To add software citations, you can use the \texttt{greatful} package's \texttt{get\_citations} function to generate the BibTeX-formatted citation for each package. Note that all of the packages have to be loaded into your working session, and listed before calling \texttt{get\_citations} for this to work.
\item
  Next, open the \texttt{pkg-refs.bib} file generated by \texttt{greatful} in a text editor like Notepad, highlight and copy the text, and then in Zotero with the collection for this project highlighted, click \texttt{File} --\textgreater{} \texttt{Import\ from\ clipboard}. Now all the software references have been added to the .bib file that will continue to be updated for this project!
\item
  Cite the software somewhere in your methods section. Here's an example:
\end{enumerate}

\begin{quote}
This paper used the free and open source R statistical computing language (R Core Team, \protect\hyperlink{ref-base}{2018}) with \texttt{tidyverse} (Wickham, \protect\hyperlink{ref-tidyverse}{2017}) software for all analysis, with the additional software packages \texttt{ggpmisc} (Aphalo, \protect\hyperlink{ref-ggpmisc}{2016}) for graphics, \texttt{gt} (Iannone et al., \protect\hyperlink{ref-gt}{2019})for tables, \texttt{here} (Müller, \protect\hyperlink{ref-here}{2017}) for file path management, \texttt{grateful} (Rodriguez-Sanchez, \protect\hyperlink{ref-grateful}{2018}) for software citation, \texttt{rmarkdown} (Allaire et al., \protect\hyperlink{ref-rmarkdown}{2018}) for interactive notebooks, and \texttt{knitr} (Xie, \protect\hyperlink{ref-knitr}{2018}), \texttt{rticles} (Allaire et al., \protect\hyperlink{ref-rticles}{2017}), and \texttt{bookdown} (Xie, \protect\hyperlink{ref-bookdown}{2016}) to create a journal-formatted PDF and other markdown and html files.
\end{quote}

\hypertarget{equations-and-math}{%
\subsection{Equations and math}\label{equations-and-math}}

@@

\hypertarget{other-packages}{%
\subsection{Other packages}\label{other-packages}}

@@

\hypertarget{writing-style}{%
\subsection{Writing style}\label{writing-style}}

@@

\begin{itemize}
\tightlist
\item
  Nature: ``Nature journals like authors to write in the active voice (`we performed the experiment\ldots{}') as experience has shown that readers find concepts and results to be conveyed more clearly if written directly.''(\emph{Nature - How to Write a Paper}, n.d.)
\item
  Science: ``Use active voice when suitable, particularly when necessary for correct syntax (e.g., `To address this possibility, we constructed a lZap library \ldots{},' not `To address this possibility, a lZap library was constructed\ldots{}').'' Ruben et al. (\protect\hyperlink{ref-rubenHowWriteScientist2012}{2012})
\end{itemize}

@@

\hypertarget{a-fun-way-to-spot-passive-voice}{%
\subsubsection{A fun way to spot passive voice:}\label{a-fun-way-to-spot-passive-voice}}

If you can add the words `by zombies' (``A Scary-Easy Way to Help You Find Passive Voice!'' \protect\hyperlink{ref-ScaryeasyWayHelp2014}{2014}) to the end of the sentence and the sentence still makes logical sense, then the sentence is in passive voice. You can also switch on the grammar settings in Microsoft Word's spelling and grammar checker and it will show up that way.

@@

\hypertarget{results}{%
\section{Results}\label{results}}

\hypertarget{scatter-plot-example}{%
\subsection{Scatter plot example}\label{scatter-plot-example}}

@@

\hypertarget{violin-plot-example}{%
\subsection{Violin plot example}\label{violin-plot-example}}

@@

\hypertarget{discussion}{%
\section{Discussion}\label{discussion}}

\hypertarget{limitations}{%
\section{Limitations}\label{limitations}}

@@

\begin{itemize}
\tightlist
\item
  Whether or not figures are included inline with text appears to depend of the version of LaTeX the document is compiled with. Compiling on a computer where TinyTeX is installed (eg in the Binder associated with the repository for this project on GitHub) will render the figures inline, whereas compiling the same document on a Windows computer with MikTeX installed does not
\item
  Does not include instructions on how to align figures
\end{itemize}

\hypertarget{conclusion}{%
\section{Conclusion}\label{conclusion}}

\hypertarget{acknowledgements}{%
\section{Acknowledgements}\label{acknowledgements}}

@@

\hypertarget{declaration-of-interest}{%
\section{Declaration of interest}\label{declaration-of-interest}}

Describe any relevant interests of the authors, particularly if there is a link to the research that is relatively uncommon and could be perceived as a conflict of interest. Otherwise : All authors declare no conflict of interest.

\hypertarget{references}{%
\section*{References}\label{references}}
\addcontentsline{toc}{section}{References}

\hypertarget{refs}{}
\leavevmode\hypertarget{ref-rticles}{}%
Allaire, J., R Foundation, Wickham, H., Journal of Statistical Software, Xie, Y., Vaidyanathan, R., Association for Computing Machinery, Boettiger, C., Elsevier, Broman, K., Mueller, K., Quast, B., Pruim, R., Marwick, B., Wickham, C., Keyes, O., \& Yu, M. (2017). \emph{Rticles: Article formats for r markdown}. \url{https://CRAN.R-project.org/package=rticles}

\leavevmode\hypertarget{ref-rmarkdown}{}%
Allaire, J., Xie, Y., McPherson, J., Luraschi, J., Ushey, K., Atkins, A., Wickham, H., Cheng, J., \& Chang, W. (2018). \emph{Rmarkdown: Dynamic documents for r}. \url{https://CRAN.R-project.org/package=rmarkdown}

\leavevmode\hypertarget{ref-ggpmisc}{}%
Aphalo, P. J. (2016). \emph{Learn r ...as you learnt your mother tongue}. Leanpub. \url{https://leanpub.com/learnr}

\leavevmode\hypertarget{ref-ScaryeasyWayHelp2014}{}%
A scary-easy way to help you find passive voice! (2014). In \emph{A scary-easy way to help you find passive voice! \textbar{} Grammarly Blog}. https://www.grammarly.com/blog/a-scary-easy-way-to-help-you-find-passive-voice/.

\leavevmode\hypertarget{ref-coakleyReviewMethodsMatch2014}{}%
Coakley, D., Raftery, P., \& Keane, M. (2014). A review of methods to match building energy simulation models to measured data. \emph{Renewable and Sustainable Energy Reviews}, \emph{37}(Supplement C), 123--141. \url{https://doi.org/10.1016/j.rser.2014.05.007}

\leavevmode\hypertarget{ref-gt}{}%
Iannone, R., Cheng, J., \& Schloerke, B. (2019). \emph{Gt: Easily create presentation-ready display tables}. \url{https://github.com/rstudio/gt}

\leavevmode\hypertarget{ref-klenbortMarkednessPerspectiveInterpretation1974}{}%
Klenbort, I., \& Anisfeld, M. (1974). Markedness and perspective in the interpretation of the active and passive voice. \emph{Quarterly Journal of Experimental Psychology}, \emph{26}(2), 189--195. \url{https://doi.org/10.1080/14640747408400404}

\leavevmode\hypertarget{ref-here}{}%
Müller, K. (2017). \emph{Here: A simpler way to find your files}. \url{https://CRAN.R-project.org/package=here}

\leavevmode\hypertarget{ref-NatureHowWrite}{}%
\emph{Nature - How to write a paper}. (n.d.). https://www.nature.com/authors/author\_resources/how\_write.html.
